### 2015-10-12 Docs/managing_jobs/managingjobs.tex
update compiler info

The code runs without any problem if it is compiled with {\tt -O2
-ftree-vectorize -fno-range-check} (our default) but with {\tt
cluster\_f.f90} compiled with {\tt -O2 -ftree-vectorize
-fno-range-check -fno-tree-pre}.  The ``{\tt fno-tree-pre}'' option
turns off ``{\tt ftree-pre}'' that is turned on by ``{\tt O2}'' \\

@@

{\tt -ftree-pre} \\
Perform partial redundancy elimination (PRE) on trees. This flag is enabled by default at {\tt -O2} and {\tt -O3}.

>>>>

The code runs without any problem if it is compiled with {\tt -O2
-ftree-vectorize -fno-range-check} (our default) but with {\tt
cluster\_f.f90} compiled with {\tt -O2 -ftree-vectorize
-fno-range-check -fno-tree-pre}.  The ``{\tt fno-tree-pre}'' option
turns off ``{\tt ftree-pre}'' that is turned on by ``{\tt O2}''

@@

\begin{quote}
{\tt -ftree-pre} \newline
Perform partial redundancy elimination (PRE) on trees. This flag is enabled by default at {\tt -O2} and {\tt -O3}.
\end{quote}

\item {\em gfortran 5.1.1}: These compilers have no known issues.
